---
title: "Bridge Project - Data Analysis Plan"
format: pdf
---

```{r}
#| include: false

library(simr)

power_simulation <- readRDS("./output/bridge-rct_power-sim.rds")

```


# Overview

This document describes the statistical analysis plan for the MI Bridge trial
and the ReDirection trial.

where relevant, we will compare these two models using a likelihood ratio test
and retain the better performing model for interpretation. we will use a
significance threshold of .05 for all tests.

Missing data will not be imputed.

For linear mixed effects models, we will use Satterthwaite degrees of freedom
for inferential tests for coefficients.

This document provides verbal descriptions for the planned analyses, and the
accompanying R script provides the base code that will be used for the analyses.

# Sample size planning

Based on the rate of recruitment in a pilot study, we estimate that each of the
two planned studies will be able to recruit approximately N = 60 participants.
To assess the statistical power of the planned studies, we conducted a
simulation based on the variance in the main outcome variable measured in the
pilot study.

This simulation suggests that with the present design, the studies would have
approximately 84% power to detect a relatively small effect of b = 0.20.

```{r}
power_simulation
```


# Study 1b: Bridge

## Primary analyses

### Treatment acceptance (care seeking)

#### Rated willingness to seek treatment

Ratings of willingness to seek treatment will be modeled with a linear mixed
effects model, with a dummy coded treatment predictor (0 = waitlist, 1 = MI),
indicating whether treatment has commenced, a time predictor (starting at 0, and
counting each weekly measurement point), and a time-since-treatment predictor
(starting at 0, and counting up at each measurement point after treatment
begins). The treatment coefficient represents the immediate effect of commencing
the treatment. The time predictor captures the overall linear effect of the
passage of time in the study, and the time-since-treatment coefficient captures
the linear effect of spending time in the treatment.

### Motivation for change

Responses on the Change Questionnaire will be modeled using a mixed-effects
model like the one above used for rated willingness to seek treatment.

## Secondary analyses

### Do you think you will actually seek care? (dichotomous)

Responses to the dichotomous question of whether the participant intents to seek
treatment in the next month will be modeled using a mixed-effects model like the
one above used for rated willingness to seek treatment. However, this model will
be a logistic regression, rather than a linear regression.

### Sexual urges (SSAS)

Scores on the SSAS will be modeled using a mixed-effects model like the one
above used for rated willingness to seek treatment.

### CSAM usage

Self-reported CSAM usage, measured by the SChiMRA+ (total number of reported
hours per week), will be modeled using a mixed-effects model like the one above
used for rated willingness to seek treatment.

### Depression (PHQ-9)

Scores on the PHQ-9 are measured pre-treatment and post-treatment. These scores
will be modeled in a series of linear mixed effects models. The first model will
use fixed predictors for treatment condition and an indicator for the timing of
the measurement (pre and post), with random intercepts for each participant. The
second model will add the interaction between the two fixed predictors. We will
compare the models and retain the better fitting one.

### Mediating effect of MI on primary outcomes through motivational talk

We will examine the potential mediating role of motivational talk on willingness
to seek care and motivation to change. To do so, we will take a mixed effects
longitudinal mediation approach (similar to that of Park et al, 2017,
10.1037/dev0000235), wherein we will fit mixed effects models predicting the
mediator and outcome variables using  dummy coded treatment predictor (0 =
waitlist, 1 = MI), indicating whether treatment has commenced, a time predictor
(starting at 0, and counting each weekly measurement point), and a
time-since-treatment predictor (starting at 0, and counting up at each
measurement point after treatment begins). We will then estimate the indirect
effect of time-since-treatment through motivational talk on the outcome
variables, using parametric bootstrapping. The mediator will be person mean
centered for these models, in order to capture the within-person effects.

### Dynamic risk (ACUTE-2007)

Scores on the ACUTE-2007 will be modeled using a mixed-effects model like the
one above used for rated willingness to seek treatment.

### Hypersexuality (HBI-19)

Scores on the PHQ-9 are measured pre-treatment and post-treatment. These scores
will be modeled with an approach like those used for the PHQ-9 scores above.

# Study 2b: ReDirection

## Sample size planning

## Primary analyses

### Sexual urges (SSAS)

scores on the ssas will be modeled with a linear mixed effects model, with a
dummy coded treatment predictor (0 = waitlist, 1 = redirection), indicating
whether treatment has commenced, a time predictor (starting at 0, and counting
each weekly measurement point), and a time-since-treatment predictor (starting
at 0, and counting up at each measurement point after treatment begins). the
treatment coefficient represents the immediate effect of commencing the
treatment. the time predictor captures the overall linear effect of the passage
of time in the study, and the time-since-treatment coefficient captures the
linear effect of spending time in the treatment.

### CSAM usage

Self-reported CSAM usage will be modeled using a mixed-effects model like the
one above used for SSAS scores.

### SChiMRA B (Behaviors against children)

#### Socialize

Self-reported socialization with children (total number of hours in the last
week) will be modeled using a mixed-effects model like the one above used for
SSAS scores.

#### Interact

Self-reported interacting with children (total number of hours in the last
week) will be modeled using a mixed-effects model like the one above used for
SSAS scores.

### Depression (PHQ-9)

Scores on the PHQ-9 are measured pre-treatment and post-treatment. These scores
will be modeled in a series of linear mixed effects models. The first model will
use fixed predictors for treatment condition and an indicator for the timing of
the measurement (pre and post), with random intercepts for each participant. The
second model will add the interaction between the two fixed predictors. We will
compare the models and retain the better fitting one.

## Secondary analyses

### Dynamic risk (ACUTE-2007)

Scores on the ACUTE-2007 will be modeled using a mixed-effects model like the
one above used for SSAS scores.

### Hypersexuality (HBI-19)

Scores on the PHQ-9 are measured pre-treatment and post-treatment. These scores
will be modeled with an approach like those used for the PHQ-9 scores above.

### Mediating effect of treatment on CSAM usage through sexual urges (SSAS)

We will examine the potential mediating role of sexual urges on the use of CSAM.
To do so, we will take a mixed effects longitudinal mediation approach (similar
to that of Park et al, 2017, 10.1037/dev0000235), wherein we will fit mixed
effects models predicting the mediator and outcome variables using  dummy coded
treatment predictor (0 = waitlist, 1 = ReDirection), indicating whether
treatment has commenced, a time predictor (starting at 0, and counting each
weekly measurement point), and a time-since-treatment predictor (starting at 0,
and counting up at each measurement point after treatment begins). We will then
estimate the indirect effect of time-since-treatment through motivational talk
on the outcome variables, using parametric bootstrapping. The mediator will be
person mean centered for these models, in order to capture the within-person
effects.