---
title: "Bridge Project - Data Analysis Plan"
format: pdf
---

```{r}
#| include: false

library(simr)

power_simulation <- readRDS("./output/bridge-rct_power-sim.rds")
power_simulation_ssas <- readRDS("./output/bridge-rct_ssas_power-sim.rds")

```


# Overview

This document describes the statistical analysis plan for the MI Bridge trial
and the ReDirection trial.

where relevant, we will compare these two models using a likelihood ratio test
and retain the better performing model for interpretation. we will use a
significance threshold of .05 for all tests.

Missing data will not be imputed. We will use all valid data from participants,
including those who drop out of the study.

For linear mixed effects models, we will use Satterthwaite degrees of freedom
for inferential tests for coefficients.

This document provides verbal descriptions for the planned analyses, and the
accompanying R script provides the base code that will be used for the analyses.

# Sample size planning

Based on the rate of recruitment in a pilot study, we estimate that it will be
feasible for each of the two planned studies to recruit approximately N = 60
participants. To assess the statistical power of the planned studies, using this
sample size, we conducted a simulation based on the variance in the main outcome
variables measured in the pilot study (specifically, motivation to seek care and
SSAS sum scores). In these simulations, we assessed the primary model used to
examine this outcome measure (described below).

The simulation addressing motivation to seek care suggests that with the
present design, the study would have approximately 83% power to detect a
relatively small effect of b = 0.25 for the effect of time spent in treatment.

```{r}
power_simulation
```

In short, the planned study will have adequate power for modestly sized
effects on motivation to seek care (primary outcome in Study 1b).

The simulation addressing SSAS sum scores suggests that with the present design,
the studies would have approximately 98% power to detect a relatively small
effect of b = 1.50 for the effect of time spent in treatment.

```{r}
power_simulation_ssas
```

In short, the planned studies will have adequate power for modestly sized
effects on motivation to seek care (primary outcome in Study 2b and a secondary
outcome in Study 1b).

We will recruit participants until we have reached a total of N = 60 non-dropout
participants for each study (Study 1b and Study 2b). For Study 1b, we define a
"dropout" as someone who takes part in fewer than 1 weekly measurement. For
Study 2b, we define a "dropout" as someone who takes part in fewer than 2 weekly
measures.

# Study 1b: Bridge

## Primary analyses

### Treatment acceptance (care seeking)

#### Rated motivation to seek treatment

Ratings of motivation to seek treatment will be modeled with a linear mixed
effects model, with a dummy coded treatment predictor (0 = waitlist, 1 = MI),
indicating whether treatment has commenced, a time predictor (starting at 0, and
counting each weekly measurement point), and a time-since-treatment predictor
(starting at 0, and counting up at each measurement point after treatment
begins). The treatment coefficient represents the immediate effect of commencing
the treatment. The time predictor captures the overall linear effect of the
passage of time in the study, and the time-since-treatment coefficient captures
the linear effect of spending time in the treatment.

### Motivation for change

Responses on the Change Questionnaire will be modeled using a mixed-effects
model like the one above used for rated motivation to seek treatment.

## Secondary analyses

### Do you think you will actually seek care? (dichotomous)

Responses to the dichotomous question of whether the participant intents to seek
treatment in the next month will be modeled using a mixed-effects model like the
one above used for rated motivation to seek treatment. However, this model will
be a logistic regression, rather than a linear regression.

### Sexual urges (SSAS)

Scores on the SSAS will be modeled using a mixed-effects model like the one
above used for rated motivation to seek treatment.

### CSAM usage

Self-reported CSAM usage, measured by the SChiMRA+ (total number of reported
hours per week), will be modeled using a mixed-effects model like the one above
used for rated motivation to seek treatment.

### Depression (PHQ-9)

Scores on the PHQ-9 are measured pre-treatment and post-treatment. These scores
will be modeled in a series of linear mixed effects models. The first model will
model fixed effects for treatment condition and an indicator for the timing of
the measurement (pre and post), with random intercepts for each participant. The
second model will add the interaction between the two fixed effects (i.e.,
condition and timing of measurement). We will compare the models and retain the
better fitting one.

### Mediating effect of MI on motivation to seek treatment through motivation to change

We will examine the potential mediating role of motivation to change (Change
Questionnaire) on motivation to seek care and whether the participants
indicates they are likely to actually seek care (dichotomous). To do so, we will
take a mixed effects longitudinal mediation approach (similar to that of Park et
al, 2017, 10.1037/dev0000235), wherein we will fit mixed effects models
predicting the mediator and outcome variables using  dummy coded treatment
predictor (0 = waitlist, 1 = MI), indicating whether treatment has commenced, a
time predictor (starting at 0, and counting each weekly measurement point), and
a time-since-treatment predictor (starting at 0, and counting up at each
measurement point after treatment begins). We will then estimate the indirect
effect of time-since-treatment through motivation to change on the outcome
variables, using parametric bootstrapping. The mediator will be person mean
centered for these models, in order to capture the within-person effects.

### Dynamic risk (ACUTE-2007)

Scores on the ACUTE-2007 will be modeled using a mixed-effects model like the
one above used for rated motivation to seek treatment.

### Hypersexuality (HBI-19)

Scores on the HBI-19 are measured pre-treatment and post-treatment. These scores
will be modeled with an approach like those used for the PHQ-9 scores above.

### Moderating effect of autistic traits (RAADS-14) on treatment effectiveness

We will examine the potential moderating role of autistic traits (measured by
the RAADS-14, at baseline) on the effectiveness of the treatment on the primary
outcomes (motivation to change and motivation to seek treatment). For each
variable, we will fit two linear mixed effects models: in the first, we will add
grand mean centered RAADS-14 sum scores as a predictor to the model used to
assess the effect of the treatment on the primary outcomes (see above); in the
second, we will add two-way interaction terms between RAADS-14 sum scores and
the dummy coded treatment predictor (0 = waitlist, 1 = MI) and the
time-since-treatment predictor (starting at 0, and counting up at each
measurement point after treatment begins). For each outcome variable, we will
compare the base model used to assess each outcome (see above) and these two
additional models and retain the best performing model for interpretation.

# Study 2b: ReDirection

## Sample size planning

## Primary analyses

### Sexual urges (SSAS)

scores on the SSAS will be modeled with a linear mixed effects model, with a
dummy coded treatment predictor (0 = waitlist, 1 = redirection), indicating
whether treatment has commenced, a time predictor (starting at 0, and counting
each weekly measurement point), and a time-since-treatment predictor (starting
at 0, and counting up at each measurement point after treatment begins). the
treatment coefficient represents the immediate effect of commencing the
treatment. the time predictor captures the overall linear effect of the passage
of time in the study, and the time-since-treatment coefficient captures the
linear effect of spending time in the treatment.

### CSAM usage

Self-reported CSAM usage will be modeled using a mixed-effects model like the
one above used for SSAS scores.

### SChiMRA B (Other behaviors related to sexual interest in children)

Self-reported interactingbehaviors related to sexual interest in children (total
number of hours in the last week) will be modeled using a mixed-effects model
like the one above used for SSAS scores.

### Depression (PHQ-9)

Scores on the PHQ-9 are measured pre-treatment and post-treatment. These scores
will be modeled in a series of linear mixed effects models. The first model will
use fixed predictors for treatment condition and an indicator for the timing of
the measurement (pre and post), with random intercepts for each participant. The
second model will add the interaction between the two fixed predictors. We will
compare the models and retain the better fitting one.

## Secondary analyses

### Dynamic risk (ACUTE-2007)

Scores on the ACUTE-2007 will be modeled using a mixed-effects model like the
one above used for SSAS scores.

### Hypersexuality (HBI-19)

Scores on the PHQ-9 are measured pre-treatment and post-treatment. These scores
will be modeled with an approach like those used for the PHQ-9 scores above.

### Mediating effect of treatment on CSAM usage through sexual urges (SSAS)

We will examine the potential mediating role of sexual urges on the use of CSAM.
To do so, we will take a mixed effects longitudinal mediation approach (similar
to that of Park et al, 2017, 10.1037/dev0000235), wherein we will fit mixed
effects models predicting the mediator and outcome variables using  dummy coded
treatment predictor (0 = waitlist, 1 = ReDirection), indicating whether
treatment has commenced, a time predictor (starting at 0, and counting each
weekly measurement point), and a time-since-treatment predictor (starting at 0,
and counting up at each measurement point after treatment begins). We will then
estimate the indirect effect of time-since-treatment through SSAS scores on CSAM
usage, using parametric bootstrapping. The mediator will be person mean centered
for these models, in order to capture the within-person effects.

### Moderating effect of autistic traits (RAADS-14) on treatment effectiveness

We will examine the potential moderating role of autistic traits (measured by
the RAADS-14, at baseline) on the effectiveness of the treatment on the primary
outcome (SSAS scores). We will fit two linear mixed effects models: in the
first, we will add grand mean centered RAADS-14 sum scores as a predictor to the
model used to assess the effect of the treatment on the primary outcomes (see
above); in the second, we will add two-way interaction terms between RAADS-14
sum scores and the dummy coded treatment predictor (0 = waitlist, 1 =
ReDirection) and the time-since-treatment predictor (starting at 0, and counting
up at each measurement point after treatment begins). We will compare the base
model used to assess each outcome (see above) and these two additional models
and retain the best performing model for interpretation.
